% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Grant R. Kurtz}
% \address used twice to have two lines of address
\address{2569 Nathaniel Rochester Hall, Rochester, NY 14623}
\address{kurtz.grant@gmail.com |  (203) 240-7149}

 
\begin{resume}
 
\section{OBJECTIVE}       A Co-Op in software development that challenges and pushes my understanding of software development and 
				technical problem solving for the Summer and Fall of 2012.
 
 
\section{EDUCATION} {\sl Bachelor of Computer Science} \\
	 Rochester Institute of Technology, Rochester, NY,  expected May 2014 \\
	GPA: 3.13 \\
	Minor: Economics 
 
\section{SKILLS} {\sl Languages:} Java, PHP, C, C++, X86, MIPS. \\
		{\sl Software:} IntelliJ Idea, Eclipse, MySQL, Git, Vim, Mercurial, JUnit, Memcache. \\
		{\sl Operating Systems:} Windows, Ubuntu, Gentoo, Slackware.
 
\section{EXPERIENCE} {\sl Lead Web Developer} \hfill Summers 2009-2011 \\
                Datto Inc., 
                101 Merritt 7, 7th Floor, Norwalk, CT 06851
                 \begin{itemize}  \itemsep -2pt % reduce space between items
	\item Managed the transition of our ticketing system from an In-House solution.
	\item Designed and worked on creating a new invoicing system using OOPHP.
	\item Interfaced with partners to determine development needs.
	\item Autotask and ConnectWise integration for partners.
	\item Various data aggregation and administrative information pages.
	\item Managed the development efforts of up to three interns.
	\end{itemize}

\section{RELATED \\ CLASSES} {\sl Rochester Institute of Technology} \hfill 2009-2012
                 \begin{itemize}  \itemsep -2pt % reduce space between items
	\item Computer Organization, Software Engineering 361, Operating Systems I, Intro to CS Theory, 
		Calculus, Probability, Discrete Math I-II, Computer Science I-IV, Programming Language Concepts,
		Professional Communications, Systems Programming I, Database Concepts
	\item Current: Systems Programming II, University Physics III, Multivariable Calculus
	\end{itemize}
 
 
\section{PROJECTS}  

	{\sl Pizza Delivery System (Java)} \\
	Software Engineering 361 project for a team of five group members.
	  \begin{itemize}  \itemsep -2pt % reduce space between items
	\item Development Lead for our team; designed and oversaw implementation.
	\item Various documentation forms, such as UML, Sequence Diagrams, AutoDoc, and Use Cases to manage the code base.
	\item Had to manage the efforts of team mates and break up project into chunks for rapid development.
	\item Primary design pattern was a Producer-Consumer Model, backed by priority queues.
	\item https://github.com/grnt426/PizzaDeliverySystem
                \end{itemize}

	{\sl Optimal Business Time Partitioning (Java)} \\
	Genetic Algorithm to find an optimal arrangement of tasks in a day.
	  \begin{itemize}  \itemsep -2pt % reduce space between items
	\item The goal of the simulation was to maximize net profit after 100 days of simulation.
	\item A GUI allowed for on-the-fly changes of the simulation.
	\item Created interactive graphs for various information to show species evolution.
	\item https://github.com/grnt426/Optimal-Business-Time-Partitioning
                \end{itemize}

	 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it Evaluations Director}, Computer Science House, Fall-Spring 2011-2012 \\
	{\it Co-Research and Development Director}, Computer Science House, Spring 2011

 

\end{resume}
\end{document}







